Visual inference for networks

### 2016-03-10 paper/network-inference.Rnw
more examples of effects

\par Estimation and implementation of these models can be done in the RSIENA software~\cite{RSiena}.  The software allows many possible effects to be included in this type of model. Some of the network effects and actor effects we look at are: 
\begin{table}  
  \begin{tabular}{llc}
  Name & Type & Formula \\ 
  \hline
  period 1 rate & Rate & $\rho_1$ \\
  outdegree & Structural & $s_{i1}(x) = \sum_j x_{ij}$ \\
  reciprocity & Structural & $s_{i2}(x) = \sum_j x_{ij}x_{ji} $
  \end{tabular}
\end{table}

>>>>

\par Estimation and implementation of these models can be done in the RSIENA software~\cite{RSiena}.  The software allows many possible effects to be included in this type of model. Some of the network effects and actor effects that are possible to include in SAOMs are given in Table ~\ref{tab:effects}. 
\begin{table}  
  \begin{tabular}{llc}
  Name & Type & Formula \\ 
  \hline
  period $m$ rate & Rate & $\rho_{m-1}$ \\
  outdegree & Structural & $s_{i1}(x) = \sum_j x_{ij}$ \\
  reciprocity & Structural & $s_{i2}(x) = \sum_j x_{ij}x_{ji} $ \\
  transitive triplets & Structural & $s_{i3}(x) = \sum_{j,h} x_{ij}x_{jh}x_{ih}$

  \end{tabular}
  \caption{\label{tab:effects}}
\end{table}
